### 2023-02-25 main/chapter_2ljets.tex
enlarge figures; progress to p110

% signal region plots
\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_sr_high_8_met_sig.pdf}
\caption{SR-High-8}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_sr_llbb_mbb.pdf}
\caption{\srllbb}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_sr_int_met_sig.pdf}
\caption{SR-Int}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_sr_low_met_sig.pdf}
\caption{SR-Low}
\end{subfigure}
\caption[
Example signal region histograms with benchmark signal sample yields overlaid
]{%
Example signal region histograms with benchmark signal sample yields overlaid
as dotted lines~\cite{atlas2022searches}.
Physically, signal yields would add on top of the backgrounds.
Unblinded data are shown --- regions in the top two plots observe zero data
and the error bars for zero events are hidden for aesthetic reasons.%
}
\label{fig:2ljets_signal_examples}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_rjr_23l_2l_summary.png}
\caption{$2\ell$ RJR~\cite{atlas_rjr_23l_SUSY_2017_03}}
\label{fig:2ljets_rjr_summaries_2017_2l}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_rjr_23l_3l_summary.png}
\caption{$3\ell$ RJR~\cite{atlas_rjr_23l_SUSY_2017_03}}
\label{fig:2ljets_rjr_summaries_2017_3l}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.9\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_rjr_summary_log.pdf}
\caption{$\twoljets$-RJR~\cite{atlas2022searches}}
\label{fig:2ljets_rjr_summaries_2ljets}
\end{subfigure}
\caption[
Summary plots for RJR searches
]{%
Summary plots for RJR searches:
(a) and (b)~two- and three- lepton selections, respectively,
\emph{reproduced from}~\cite{atlas_rjr_23l_SUSY_2017_03},
(c)~all regions from the $\twoljets$-RJR search~\cite{atlas2022searches}.
Note the excesses in
$\mathrm{SR}2\ell\_\mathrm{Low}$ and $\mathrm{SR}2\ell\_\mathrm{ISR}$ of (a),
and in
$\mathrm{SR}3\ell\_\mathrm{Low}$ and $\mathrm{SR}3\ell\_\mathrm{ISR}$ of (b).
\emph{Sub-figure (c) was made by the RJR team.}
}
\label{fig:2ljets_rjr_summaries}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRllbb.png}
\caption{\srllbb, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mbb_SRllbb.png}
\caption{\srllbb, $\mbb$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRllbb.png}
\caption{VR-$\llbb$, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mbb_VRllbb.png}
\caption{VR-$\llbb$, $\mbb$}
\end{subfigure}
\caption[
Pre-fit distributions in $\llbb$ signal and validation regions
]{%
Pre-fit distributions in $\llbb$ signal and validation regions.
Signal regions are unblinded.
Errors are statistical.
}
\label{fig:2ljets_high_llbb_region}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_VRHigh.png}
\caption{VR-High, $\mjj$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_VRHighR.png}
\caption{VR-High-R, $\mjj$}
\end{subfigure}
\caption[
Pre-fit $\mjj$ distributions in validation regions VR-High and VR-High-R
]{%
Pre-fit $\mjj$ distributions in validation regions VR-High and VR-High-R.
Signal regions are unblinded.
Errors are statistical.
The apparent excess at low $\mjj$ in VR-High is not well understood.
}
\label{fig:2ljets_high_mjj_vrhigh}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.48\textwidth]{figures/2ljets_vr_llbb_met_sig.pdf}
\caption[
Post-fit $\metsig$ distribution in VR-$\llbb$
]{%
Post-fit $\metsig$ distribution in VR-$\llbb$ with all statistical and
systematic uncertainties~\cite{atlas2022searches}.
Backgrounds are fitted to control and signal regions.
This region is also displayed pre-fit with coarser bins in
Figure~\ref{fig:2ljets_high_llbb_region}.
}
\label{fig:2ljets_high_metsig_vrllbb_paper}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRInt.png}
\caption{SR-Int, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_SRInt.png}
\caption{SR-Int, $\mjj$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRInt.png}
\caption{VR-Int, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_VRInt.png}
\caption{VR-Int, $\mjj$}
\end{subfigure}
\caption[
Pre-fit distributions in Intermediate signal and validation regions
]{%
Pre-fit distributions in Intermediate signal and validation regions.
Signal regions are unblinded.
Errors are statistical.
}
\label{fig:2ljets_int_region}
\end{figure}

The control region \crvz\ occupies the $\mjj$ sideband of SR-Int and VR-Int.
As seen from Figure~\ref{fig:2ljets_int_cr_region}, the selections in this
intermediate space give \crvz\ a very pure \diboson\ background, which is
valuable to constrain our modelling by extrapolation to High regions.
Also included in Table~\ref{tab:2ljets_int} and
Figure~\ref{fig:2ljets_int_cr_region} is \crtt, which uses various other
selections of $b$-tagged data to constrain $\ttbar$ backgrounds.
Both control regions show good agreement pre-fit and with statistical uncertainties
only.
\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_CRZZ.png}
\caption{\crvz, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_CRZZ.png}
\caption{\crvz, $\mjj$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_CRtt.png}
\caption{\crtt, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_CRtt.png}
\caption{\crtt, $\mjj$}
\end{subfigure}
\caption[
Pre-fit distributions in the control regions CR-tt and CR-VZ
]{%
Pre-fit distributions in the control regions \crtt\ and \crvz.
Errors are statistical.
}
\label{fig:2ljets_int_cr_region}
\end{figure}

Some figures label \crvz\ as `\crz Z'; the region was renamed late in this
analysis project when it was show to contain substantial fractions of
$W\kern-0.4exZ$ as well as $ZZ$, as illustrated in
Figure~\ref{fig:2ljets_splits} of
Section~\ref{sec:2ljets_validation}.

\subsection{Low}
\label{sec:2ljets_low}
In Low regions, which have $\metsig \in 6\textrm{--}12$, the $\zjets$
background becomes large since its fake $\met$, which arises from
from mismeasurements or rare interactions, is no longer eliminated.
Backgrounds from $\ttbar$ similarly increase, and the selections inherited from
Intermediate regions are no longer sufficient.

@@

Boosted $Z\to \ell\ell$ decays will tend to have small $\rll$.
Similarly to $\rjj$ in the High regions, this can usefully select signals,
but here also works to reject other $\ell\ell$ production mechanisms which
produce leptons in less correlated directions, particularly dileptonic
$\ttbar$.
As elsewhere, sensitivity is increased by binning SR-Low with
to form SR-Low-a with $\metsig \in 6\textrm{--}9$ and
SR-Low-b $\metsig \in 9\textrm{--}12$.

To remove some observed mis-modelling of backgrounds, Low regions require
exactly two jets.
Abandoned region designs which used more jets are discussed below in
Section~\ref{sec:2ljets_low_isr}.

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_low_Rll_SRLow_noRll.pdf}
\caption{SR-Low$/\{\rll\}$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_low_mt2leplsp_0_SRLow_noRll_nomt2.pdf}
\caption{SR-Low$/\{\rll,\mttwoll\}$}
\label{fig:2ljets_low_minus_norll_nomt2_mt2}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_low_absdPhiPllMet_SRLow2_noDphi.pdf}
\caption{SR-Low-2$/\{\dphillmet\}$}
\label{fig:2ljets_low_minus_dphi}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_low_absdPhiPllMet_SRLow2_noDphi_mg5.pdf}
\caption{SR-Low-2$/\{\dphillmet\}$ (alt)}
\label{fig:2ljets_low_minus_dphi_alt}
\end{subfigure}
\caption[
Relaxed versions of SR-Low and SR-Low-2 to motivate their angular selections
]{%
Relaxed versions of SR-Low and SR-Low-2 to motivate their angular selections.
Each removes requirements listed in Table~\ref{tab:2ljets_low}:
(a) SR-Low removes $\rll$,
(b) SR-Low removes $\rll$ and $\mttwoll$,
and
(c, d) SR-Low-2 removes $\dphillmet$.
\\[0.5em]
Signals trend towards small $\rll$, plausibly due to their more boosted
$Z\to \ell\ell$ decays; small $\rll$ also suppresses $\ttbar$.
The mass of signals seen at small $\mttwoll$ in (b) motivates the design of
SR-Low-2.
Signals in SR-Low-2 spike at small $\dphillmet$ in (c); better statistical
precision is provided by an alternative $\zjets$ sample in (d).
}
\label{fig:2ljets_low_minus}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRLow.png}
\caption{SR-Low, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_SRLow.png}
\caption{SR-Low, $\mjj$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRLow.png}
\caption{VR-Low, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_VRLow.png}
\caption{VR-Low, $\mjj$}
\end{subfigure}
\caption[
Pre-fit distributions in Low signal and validation regions
]{%
Pre-fit distributions in Low signal and validation regions.
Signal regions are unblinded.
Errors are statistical.
}
\label{fig:2ljets_low_region}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRLow2.png}
\caption{SR-Low-2, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_SRLow2.png}
\caption{SR-Low-2, $\mjj$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRLow2.png}
\caption{VR-Low-2, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_VRLow2.png}
\caption{VR-Low-2, $\mjj$}
\end{subfigure}
\caption[
Pre-fit distributions in Low-2 signal and validation regions
]{%
Pre-fit distributions in Low-2 signal and validation regions.
Signal regions are unblinded.
Errors are statistical.
}
\label{fig:2ljets_low2_region}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_CRZ.png}
\caption{\crz, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_CRZ.png}
\caption{\crz, $\mjj$}
\end{subfigure}
\caption[
Pre-fit distributions in the control region CR-Z
]{%
Pre-fit distributions in the control region \crz.
Errors are statistical.
}
\label{fig:2ljets_low_cr_region}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrlow_old_srlowisr.png}
\caption{SR-Low-ISR, $\ptisr$ (blind)}
\label{fig:2ljets_low_isr_old_sr}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrlow_old_vrlowisr.png}
\caption{VR-Low-ISR, $\mwisr$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrlow_old_crlowisr.png}
\caption{CR-Low-ISR, $\mwisr$}
\end{subfigure}
\caption[
Pre-fit distributions in draft Low-ISR regions, which were removed
]{%
Pre-fit distributions in draft Low-ISR regions, which were removed and never
unblinded.
These regions required hard jets directed away from the leptons and $\ptmiss$.
As seen from (b) and (c), the background modelling is poor and in conflict
with normalization factors in other control regions.
Variables and regions are defined in the text of
Section~\ref{sec:2ljets_low_isr}.
Errors are statistical.
}
\label{fig:2ljets_low_isr_old}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrlow_old_crlowisr_z.png}
\caption{CR-Low-ISR-Z, $\mwisr$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrlow_old_crlowisr_df.png}
\caption{CR-Low-ISR-DF, $\mwisr$}
\end{subfigure}
\caption[
Pre-fit distributions in extra draft Low-ISR control regions, which were
removed
]{%
Pre-fit distributions in extra draft Low-ISR control regions, which were
removed.
These regions required hard jets directed away from the leptons and $\ptmiss$.
Variables and regions are defined in the text of
Section~\ref{sec:2ljets_low_isr}.
Errors are statistical.
}
\label{fig:2ljets_low_isr_old_more}
\end{figure}

>>>>

% signal region plots
\begin{figure}[tp]
\centering
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_sr_high_8_met_sig.pdf}
\caption{SR-High-8}
\end{subfigure}
\hfill
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_sr_llbb_mbb.pdf}
\caption{\srllbb}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_sr_int_met_sig.pdf}
\caption{SR-Int}
\end{subfigure}
\hfill
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_sr_low_met_sig.pdf}
\caption{SR-Low}
\end{subfigure}
\caption[
Example signal region histograms with benchmark signal sample yields overlaid
]{%
Example signal region histograms with benchmark signal sample yields overlaid
as dotted lines~\cite{atlas2022searches}.
Physically, signal yields would add on top of the backgrounds.
Unblinded data are shown --- regions in the top two plots observe zero data
and the error bars for zero events are hidden for aesthetic reasons.%
}
\label{fig:2ljets_signal_examples}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_rjr_23l_2l_summary.png}
\caption{$2\ell$ RJR~\cite{atlas_rjr_23l_SUSY_2017_03}}
\label{fig:2ljets_rjr_summaries_2017_2l}
\end{subfigure}
\hfill
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_rjr_23l_3l_summary.png}
\caption{$3\ell$ RJR~\cite{atlas_rjr_23l_SUSY_2017_03}}
\label{fig:2ljets_rjr_summaries_2017_3l}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.9\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_rjr_summary_log.pdf}
\caption{$\twoljets$-RJR~\cite{atlas2022searches}}
\label{fig:2ljets_rjr_summaries_2ljets}
\end{subfigure}
\caption[
Summary plots for RJR searches
]{%
Summary plots for RJR searches:
(a) and (b)~two- and three- lepton selections, respectively,
\emph{reproduced from}~\cite{atlas_rjr_23l_SUSY_2017_03},
(c)~all regions from the $\twoljets$-RJR search~\cite{atlas2022searches}.
Note the excesses in
$\mathrm{SR}2\ell\_\mathrm{Low}$ and $\mathrm{SR}2\ell\_\mathrm{ISR}$ of (a),
and in
$\mathrm{SR}3\ell\_\mathrm{Low}$ and $\mathrm{SR}3\ell\_\mathrm{ISR}$ of (b).
\emph{Sub-figure (c) was made by the RJR team.}
}
\label{fig:2ljets_rjr_summaries}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRllbb.png}
\caption{\srllbb, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mbb_SRllbb.png}
\caption{\srllbb, $\mbb$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRllbb.png}
\caption{VR-$\llbb$, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mbb_VRllbb.png}
\caption{VR-$\llbb$, $\mbb$}
\end{subfigure}
\caption[
Pre-fit distributions in $\llbb$ signal and validation regions
]{%
Pre-fit distributions in $\llbb$ signal and validation regions.
Signal regions are unblinded.
Errors are statistical.
}
\label{fig:2ljets_high_llbb_region}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_VRHigh.png}
\caption{VR-High, $\mjj$}
\end{subfigure}
\hfill
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_VRHighR.png}
\caption{VR-High-R, $\mjj$}
\end{subfigure}
\caption[
Pre-fit $\mjj$ distributions in validation regions VR-High and VR-High-R
]{%
Pre-fit $\mjj$ distributions in validation regions VR-High and VR-High-R.
Signal regions are unblinded.
Errors are statistical.
The apparent excess at low $\mjj$ in VR-High is not well understood.
}
\label{fig:2ljets_high_mjj_vrhigh}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.62\textwidth]{figures/2ljets_vr_llbb_met_sig.pdf}
\caption[
Post-fit $\metsig$ distribution in VR-$\llbb$
]{%
Post-fit $\metsig$ distribution in VR-$\llbb$ with all statistical and
systematic uncertainties~\cite{atlas2022searches}.
Backgrounds are fitted to control and signal regions.
This region is also displayed pre-fit with coarser bins in
Figure~\ref{fig:2ljets_high_llbb_region}.
}
\label{fig:2ljets_high_metsig_vrllbb_paper}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRInt.png}
\caption{SR-Int, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_SRInt.png}
\caption{SR-Int, $\mjj$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRInt.png}
\caption{VR-Int, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_VRInt.png}
\caption{VR-Int, $\mjj$}
\end{subfigure}
\caption[
Pre-fit distributions in Intermediate signal and validation regions
]{%
Pre-fit distributions in Intermediate signal and validation regions.
Signal regions are unblinded.
Errors are statistical.
}
\label{fig:2ljets_int_region}
\end{figure}

The control region \crvz\ occupies the $\mjj$ sideband of SR-Int and VR-Int.
As seen from Figure~\ref{fig:2ljets_int_cr_region}, the selections in this
intermediate space give \crvz\ a very pure \diboson\ background, which is
valuable to constrain our modelling by extrapolation to High regions.
Also included in Table~\ref{tab:2ljets_int} and
Figure~\ref{fig:2ljets_int_cr_region} is \crtt, which uses various other
selections of $b$-tagged data to constrain $\ttbar$ backgrounds.
Both control regions show good agreement pre-fit and with statistical uncertainties
only.
\begin{figure}[tp]
\centering
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_CRZZ.png}
\caption{\crvz, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_CRZZ.png}
\caption{\crvz, $\mjj$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_CRtt.png}
\caption{\crtt, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_CRtt.png}
\caption{\crtt, $\mjj$}
\end{subfigure}
\caption[
Pre-fit distributions in the control regions CR-tt and CR-VZ
]{%
Pre-fit distributions in the control regions \crtt\ and \crvz.
Errors are statistical.
}
\label{fig:2ljets_int_cr_region}
\end{figure}

Some figures label \crvz\ as `\crz Z'; the region was renamed late in this
analysis project when it was shown to contain substantial fractions of
$W\kern-0.4exZ$ as well as $ZZ$, as illustrated in
Figure~\ref{fig:2ljets_splits} of
Section~\ref{sec:2ljets_validation}.

\subsection{Low}
\label{sec:2ljets_low}
In Low regions, which have $\metsig \in 6\textrm{--}12$, the $\zjets$
background becomes large since its fake $\met$, which arises from
mismeasurements or rare interactions, is no longer eliminated.
Backgrounds from $\ttbar$ similarly increase, and the selections inherited from
Intermediate regions are no longer sufficient.

@@

Boosted $Z\to \ell\ell$ decays will tend to have small $\rll$.
Similarly to $\rjj$ in the High regions, this can usefully select signals,
but here also works to reject other $\ell\ell$ production mechanisms that
produce leptons in less correlated directions, particularly dileptonic
$\ttbar$.
As elsewhere, sensitivity is increased by binning SR-Low
to form SR-Low-a with $\metsig \in 6\textrm{--}9$ and
SR-Low-b $\metsig \in 9\textrm{--}12$.

To remove some observed mis-modelling of backgrounds, Low regions require
exactly two jets.
Abandoned region designs, which used more jets, are discussed below in
Section~\ref{sec:2ljets_low_isr}.

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_low_Rll_SRLow_noRll.pdf}
\caption{SR-Low$/\{\rll\}$}
\end{subfigure}
\hfill
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_low_mt2leplsp_0_SRLow_noRll_nomt2.pdf}
\caption{SR-Low$/\{\rll,\mttwoll\}$}
\label{fig:2ljets_low_minus_norll_nomt2_mt2}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_low_absdPhiPllMet_SRLow2_noDphi.pdf}
\caption{SR-Low-2$/\{\dphillmet\}$}
\label{fig:2ljets_low_minus_dphi}
\end{subfigure}
\hfill
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_low_absdPhiPllMet_SRLow2_noDphi_mg5.pdf}
\caption{SR-Low-2$/\{\dphillmet\}$ (alt)}
\label{fig:2ljets_low_minus_dphi_alt}
\end{subfigure}
\caption[
Relaxed versions of SR-Low and SR-Low-2 to motivate their angular selections
]{%
Relaxed versions of SR-Low and SR-Low-2 to motivate their angular selections.
Each removes requirements listed in Table~\ref{tab:2ljets_low}:
(a) SR-Low removes $\rll$,
(b) SR-Low removes $\rll$ and $\mttwoll$,
and
(c, d) SR-Low-2 removes $\dphillmet$.
\\[0.5em]
Signals trend towards small $\rll$, plausibly due to their more boosted
$Z\to \ell\ell$ decays; small $\rll$ also suppresses $\ttbar$.
The mass of signals seen at small $\mttwoll$ in (b) motivates the design of
SR-Low-2.
Signals in SR-Low-2 spike at small $\dphillmet$ in (c); better statistical
precision is provided by an alternative $\zjets$ sample in (d).
}
\label{fig:2ljets_low_minus}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRLow.png}
\caption{SR-Low, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_SRLow.png}
\caption{SR-Low, $\mjj$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRLow.png}
\caption{VR-Low, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_VRLow.png}
\caption{VR-Low, $\mjj$}
\end{subfigure}
\caption[
Pre-fit distributions in Low signal and validation regions
]{%
Pre-fit distributions in Low signal and validation regions.
Signal regions are unblinded.
Errors are statistical.
}
\label{fig:2ljets_low_region}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_SRLow2.png}
\caption{SR-Low-2, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_SRLow2.png}
\caption{SR-Low-2, $\mjj$}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_VRLow2.png}
\caption{VR-Low-2, $\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_VRLow2.png}
\caption{VR-Low-2, $\mjj$}
\end{subfigure}
\caption[
Pre-fit distributions in Low-2 signal and validation regions
]{%
Pre-fit distributions in Low-2 signal and validation regions.
Signal regions are unblinded.
Errors are statistical.
}
\label{fig:2ljets_low2_region}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.62\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_met_Sign_CRZ.png}
\caption{\crz, $\metsig$}
\end{subfigure}
\\
\begin{subfigure}{0.62\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_def_mjj_CRZ.png}
\caption{\crz, $\mjj$}
\end{subfigure}
\caption[
Pre-fit distributions in the control region CR-Z
]{%
Pre-fit distributions in the control region \crz.
Errors are statistical.
}
\label{fig:2ljets_low_cr_region}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrlow_old_srlowisr.png}
\caption{SR-Low-ISR, $\ptisr$ (blind)}
\label{fig:2ljets_low_isr_old_sr}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrlow_old_vrlowisr.png}
\caption{VR-Low-ISR, $\mwisr$}
\end{subfigure}
\hfill
\begin{subfigure}{0.495\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrlow_old_crlowisr.png}
\caption{CR-Low-ISR, $\mwisr$}
\end{subfigure}
\caption[
Pre-fit distributions in draft Low-ISR regions, which were removed
]{%
Pre-fit distributions in draft Low-ISR regions, which were removed and never
unblinded.
These regions required hard jets directed away from the leptons and $\ptmiss$.
As seen from (b) and (c), the background modelling is poor and in conflict
with normalization factors in other control regions.
Variables and regions are defined in the text of
Section~\ref{sec:2ljets_low_isr}.
Errors are statistical.
}
\label{fig:2ljets_low_isr_old}
\end{figure}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.62\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrlow_old_crlowisr_z.png}
\caption{CR-Low-ISR-Z, $\mwisr$}
\end{subfigure}
\\
\begin{subfigure}{0.62\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_vrlow_old_crlowisr_df.png}
\caption{CR-Low-ISR-DF, $\mwisr$}
\end{subfigure}
\caption[
Pre-fit distributions in extra draft Low-ISR control regions, which were
removed
]{%
Pre-fit distributions in extra draft Low-ISR control regions, which were
removed.
These regions required hard jets directed away from the leptons and $\ptmiss$.
Variables and regions are defined in the text of
Section~\ref{sec:2ljets_low_isr}.
Errors are statistical.
}
\label{fig:2ljets_low_isr_old_more}
\end{figure}
